### 2020-03-26 Thesis-Chapter2-Background.tex
Add more sources and notes on laws

In 1976, the same year Diffie and Hellmann published their research in public key cryptography, the U.S. Congress passed
the Arms Export Control Act and declares that strong cryptography is subject to export controls \cite{kehl_right_2015}.
In 1991, the U.S. Senate introduced, but did not pass, a bill mandating access to plain text contents when authorized by
law; in response, Philip Zimmermann released PGP (Pretty Good Privacy), a public key encryption tool to secure email, in
order that strong cryptography be ``made available to the American public before it became illegal to use''
\cite{zimmermann_1996}. In 1993, the Clinton administration introduced Clipper Chip \cite{press_1993} with the goal of
``providing the public with strong cryptographic tools without sacrificing the ability of law enforcement and
intelligence agencies to access unencrypted versions of those communications'' \cite{thompson_2015}. Citing the
foundational role of cryptography in security--and the potential of human rights abuses for compromised
privacy--industry and prominent technical leaders reacted negatively to the chip \cite{kehl_right_2015}
\cite{zimmermann_1996}. When security researcher Matt Blaze discovered flaws that allowed users to subvert the Clipper
Chip mechanisms \cite{blaze_protocol_1994}, the proposal died.

@@

From 1996 to 1999, the SAFE Act was proposed several times, had hearings, and gained support \cite{kehl_right_2015}. By
this time, there was "an overwhelming amount of evidence against moving ahead with any key escrow schemes"
\cite{thompson_2015}, and in 1999 the Clinton administration abruptly changed course, adopting almost all SAFE Act
proposals \cite{kehl_right_2015}. This development marks the end of the First Crypto War.

@@

Characteristic elements of the Second Crypto War include:
\begin{enumerate}
    \item The Apple v. FBI case over access to the San Bernardino shooter's iPhone \cite{schulze_clipper_2017}
    \item A return to the Four Horsemen \cite{schneier_scaring_2019}, with a (warranted \cite{keller_internet_2019})
            focus currently on CSAM \cite{geller_2019}
    \item "Security vs Security" vs "Security vs Privacy" \cite{stalla_bourdillon_privacy_2014} \cite{schneier_2019}
    \item Pendulating emphasis on DIM/E2E and DAR/DE \cite{schneier_2019}
    \item A political landscape marked by uncertainty, extremism, misinformation, and most recently, a pandemic that
            will have unknown impacts
\end{enumerate}

@@

\begin{itemize}
    \item The Bill of Rights: Amendments I, IV, and V \cite{madison_1791}
    \item The Arms Export Control Act (AECA) of 1976 established export controls over strong encryption techniques
        introduced ITAR (International Traffic in Arms Regulations) \cite{morgan_hr13680_1976} \cite{kehl_right_2015}
    \item The Computer Fraud and Abuse Act (CFAA) of 1986 \cite{hughes_hr4718_1986} \cite{wolff_computer_2016}
    \item The Communications Assistance for Law Enforcement Act (CALEA) of 1994 \cite{edwards_hr4922_1994}
    \item \dots
\end{itemize}

>>>>

In 1976, the same year Diffie and Hellmann published their research in public key cryptography, the U.S. Congress passed
the Arms Export Control Act and declares that strong cryptography is subject to export controls \cite{kehl_right_2015}.
In 1991, the U.S. Senate introduced, but did not pass, a bill mandating access to plain text contents when authorized by
law; in response, Philip Zimmermann released PGP (Pretty Good Privacy), a public key encryption tool to secure email, in
order that strong cryptography be ``made available to the American public before it became illegal to use''
\cite{zimmermann_1996}. In 1993, the Clinton administration introduced Clipper Chip \cite{press_1993} with the goal of
``providing the public with strong cryptographic tools without sacrificing the ability of law enforcement and
intelligence agencies to access unencrypted versions of those communications'' \cite{thompson_2015}. Citing the
foundational role of cryptography in security--and the potential of human rights abuses for compromised
privacy--industry and prominent technical leaders reacted negatively to the initiative \cite{kehl_right_2015}
\cite{zimmermann_1996}. When security researcher Matt Blaze discovered flaws that allowed users to subvert the Clipper
Chip mechanisms \cite{blaze_protocol_1994}, the proposal died.

@@

From 1996 to 1999, the SAFE Act was proposed several times, had hearings, and gained support \cite{kehl_right_2015}. By
this time, there was ``an overwhelming amount of evidence against moving ahead with any key escrow schemes''
\cite{thompson_2015}, and in 1999 the Clinton administration abruptly changed course, adopting almost all SAFE Act
proposals \cite{kehl_right_2015}. This development marks the end of the First Crypto War.

@@

Characteristic elements of the Second Crypto War include:
\begin{enumerate}
    \item The Apple v. FBI case over access to the San Bernardino shooter's iPhone \cite{schulze_clipper_2017}
    \item A return to the Four Horsemen \cite{schneier_scaring_2019}, with a (warranted \cite{keller_internet_2019})
            focus currently on CSAM \cite{geller_2019}
    \item ``Security vs Security'' vs ``Security vs Privacy'' \cite{stalla_bourdillon_privacy_2014} \cite{schneier_2019}
    \item Pendulating emphasis on DIM/E2E and DAR/DE \cite{schneier_2019}
    \item A political landscape marked by uncertainty, extremism, misinformation, and most recently, a pandemic that
            will have unknown impacts
\end{enumerate}

@@

\begin{itemize}
    \item The All Writs Act \cite{congress_1789}
    \item The Bill of Rights: Amendments I, IV, and V \cite{madison_1791}
    \item The Arms Export Control Act (AECA) of 1976 established export controls over strong encryption techniques
        introduced ITAR (International Traffic in Arms Regulations) \cite{morgan_hr13680_1976} \cite{kehl_right_2015}
    \item The Computer Fraud and Abuse Act (CFAA) of 1986 \cite{hughes_hr4718_1986} \cite{wolff_computer_2016}
    \item The Communications Assistance for Law Enforcement Act (CALEA) of 1994 \cite{edwards_hr4922_1994}
    \item \dots
\end{itemize}
